\Large\bf FlexibleSUSY --- A spectrum generator generator for supersymmetric models

### 2013-12-28 doc/paper.tex
extend tree-level spectrum calculation and fixed-point it. section

\subsection{tree level spectrum}
The diagonalised tree level $\overline{DR}$ masses are obtained from expressions...
The numerical diagonalisation is performed by... with an accuracy set by...   
\subsection{two scale fixed point iteration}
The default solver which calls the above routines above and finds the full set of $\overline{DR}$ masses in the model consistent with all constraints is the two-scale solver.  This can be selected by... but if no selection is made this will be used anyway as default.

This approach is decribed in \cite{Barger:1993gh} for the MSSM and is widely implemented in SUSY spectrum generators.

The stucture of the two-scale algorithm used in \fs is as follows,
%
Initial guess:
\begin{enumerate}
\item Guess gauge couplings $g_{1,2,3}$ at $m_Z$
\item Apply user-defined low-scale constraint (\code{LowScaleInput})
\item Guess Yukawa couplings $y^{u,d,e}_{ij}$ at $m_Z$
\item Run model to the high-scale (\code{HighScaleFirstGuess})
\item Apply high-scale constraint (\code{HighScaleInput})
\item Run model to the low-scale (\code{LowScaleFirstGuess})
\item Solve EWSB eqs.\ at the tree-level
\item Calculate \DRbar\ masses
\end{enumerate}
%
Solving the renormalization group equations:
\begin{enumerate}
\item \label{rge-step-one} Run model to the low-scale (\code{LowScale})
  \begin{enumerate}
  \item Calculate \DRbar\ masses
  \item Recalculate low-scale
  \item Calculate \DRbar\ gauge and Yukawa couplings $g_{1,2,3}$, $y^{u,d,e}_{ij}$
  \item Apply user-defined low-scale constraint (\code{LowScaleInput})
  \end{enumerate}
\item Run model to the high-scale (\code{HighScale})
  \begin{enumerate}
  \item Recalculate high-scale
  \item Apply high-scale constraint (\code{HighScaleInput})
  \end{enumerate}
\item Run model to the susy-scale (\code{SUSYScale})
  \begin{enumerate}
  \item Calculate \DRbar\ masses
  \item Recalculate low-scale
  \item Apply susy-scale constraint (\code{SUSYScaleInput})
  \item Solve EWSB eqs.\ at the one-loop level
  \end{enumerate}
\item If not converged yet, goto \ref{rge-step-one}
\end{enumerate}
%
Calculating the particle spectrum:
\begin{enumerate}
\item Run model to the susy-scale
\item Calculate the pole masses
\item Run model to the parameter output scale (SLHA block MODSEL 12)
\end{enumerate}

>>>>

\subsection{Tree-level spectrum}
The tree-level $\overline{DR}$ masses are calculated by diagonalizing
the mass matrices returned from \code{SARAH`MassMatrix[]}.  The
numerical diagonalization is performed by the Eigen library routines
\code{Eigen::JacobiSVD} and \code{Eigen::SelfAdjointEigenSolver} for
small matrices, and the Lapack routines \code{zgesvd}, \code{dgesvd},
\code{zheev}, \code{dsyev} for matrices with more than four rows and
columns.

\subsection{Two-scale fixed point iteration}
The default two-scale RG solver uses above beta functions and boundary
conditions to find the full set of $\overline{DR}$ masses in the model
consistent with all constraints.  It does so by iterating between the
scales of all boundary conditions, applying the constraints and
checking for convergence.  This approach is decribed in
\cite{Barger:1993gh} for the MSSM and is widely implemented in SUSY
spectrum generators.

The in more detail the two-scale algorithm used in \fs works as
follows:
%
\\Initial guess:
\begin{enumerate}
\item Guess gauge couplings $g_{1,2,3}$ at $m_Z$
\item Apply user-defined low-scale constraint (\code{LowScaleInput})
\item Guess Yukawa couplings $y^{u,d,e}_{ij}$ at $m_Z$
\item Run model to the high-scale (\code{HighScaleFirstGuess})
\item Apply high-scale constraint (\code{HighScaleInput})
\item Run model to the low-scale (\code{LowScaleFirstGuess})
\item Solve EWSB eqs.\ at the tree-level
\item Calculate \DRbar\ masses
\end{enumerate}
%
Solving the renormalization group equations:
\begin{enumerate}
\item \label{rge-step-one} Run model to the low-scale (\code{LowScale})
  \begin{enumerate}
  \item Calculate \DRbar\ masses
  \item Recalculate low-scale
  \item Calculate \DRbar\ gauge and Yukawa couplings $g_{1,2,3}$, $y^{u,d,e}_{ij}$
  \item Apply user-defined low-scale constraint (\code{LowScaleInput})
  \end{enumerate}
\item Run model to the high-scale (\code{HighScale})
  \begin{enumerate}
  \item Recalculate high-scale
  \item Apply high-scale constraint (\code{HighScaleInput})
  \end{enumerate}
\item Run model to the susy-scale (\code{SUSYScale})
  \begin{enumerate}
  \item Calculate \DRbar\ masses
  \item Recalculate low-scale
  \item Apply susy-scale constraint (\code{SUSYScaleInput})
  \item Solve EWSB eqs.\ at the one-loop level
  \end{enumerate}
\item If not converged yet, goto \ref{rge-step-one}
\end{enumerate}
%
Calculating the particle spectrum:
\begin{enumerate}
\item Run model to the susy-scale
\item Calculate the pole masses
\item Run model to the parameter output scale (SLHA block MODSEL 12)
\end{enumerate}
